Rust for Scientific Computing

### 2025-08-25 main.tex
deduplicate list of crates

EGObox\\
A library for evolutionary game theory and agent-based modeling. It allows researchers to
explore strategies, equilibria, and dynamics in multi-agent systems. Designed with flexibility to
model diverse game-theoretic scenarios.

@@

kifmm-rs\\
A Rust implementation of the kernel-independent fast multipole method (FMM). It
accelerates particle simulations and large-scale interactions in physics. The focus is on
high-performance computing and scalability.

@@

Polars\\
A fast DataFrame library for Rust, with APIs also available in Python. It provides
powerful data manipulation, joins, and group-by operations with performance close to Apache Arrow.
Designed for data science, analytics, and scientific workflows.

@@

oxidicom\\
A high-performance DICOM receiver for the ChRIS backend (CUBE).
\url{https://chrisproject.org/}

@@

Raphtory\\
Temporal graphs from Scala to Rust.

@@

extendr\\
Frictionless bindings for R and Rust.

@@

Polars\\
Polars is a DataFrame library for Rust. It is based on Apache Arrow’s memory model. Apache
Arrow provides very cache efficient columnar data structures and is becoming the defacto standard
for columnar data.

@@

\url{https://chrisproject.org/}\\
ChRIS is an open-source platform for computational research and medicine.

@@

faer-rs\\
A linear algebra foundation for the Rust programming language.

@@

extendr\\
Frictionless bindings for R and Rust.

Rusting\\
Rusting RSRS.

Physics\\
Physics simulations in Bevy.

An\\
An embedded memory cache for persistent memory access.

Polars\\
Polars in the factory: when databases trump collections for modeling.

Writing\\
Writing maths software in Rust after 20 years of C++: graph isomorphism and groups.

Productive\\
Productive and reliable constitutive modeling in Rust.

Efficient\\
Efficient 1-bit matrix approximations.

Developing\\
Developing Rust-based R packages using the Roxido framework.

@@

Back\\
Back to basics: rebuilding computational biomechanics crate by crate.

Cargo\ \ Cargo +GPU build: An early outlook.

Writing\\
Writing a grid library for finite and boundary element methods.

>>>>

@@

@@

@@

oxidicom\\
A high-performance DICOM receiver for the ChRIS backend (CUBE).
\url{https://chrisproject.org/}
ChRIS is an open-source platform for computational research and medicine.

@@

@@

@@

Polars\\
Polars is a DataFrame library for Rust. It is based on Apache Arrow’s memory model. Apache
Arrow provides very cache efficient columnar data structures and is becoming the defacto standard
for columnar data.\\
A fast DataFrame library for Rust, with APIs also available in Python. It provides
powerful data manipulation, joins, and group-by operations with performance close to Apache Arrow.
Designed for data science, analytics, and scientific workflows.

@@

@@

@@

@@
